Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-03-01 latex/MPP21/paper.tex
added dummy accuracy plot and data file

\author{\IEEEauthorblockN{Grey Ballard}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{ballard@wfu.edu}}
\and
\IEEEauthorblockN{Jack Weissenberger}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{jack.weissenberger@gmail.com}}
\and
\IEEEauthorblockN{Luoping\GB{?} Zhang}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{zhanl317@wfu.edu}}
}

@@

Given these two contributions to the numerical error, $\lambda$ can be optimized to balance the effects based on parameters $\sigma$ and $\varphi$ (and $d$).
As shown by Bini, Lotti, and Romani \cite{BLR80}, the optimal $\lambda$ should be set to $\Theta(2^{-d/(\sigma+\varphi)})$.
Using this value of $\lambda$, the numerical error incurred by the algorithm will be bounded by $O(2^{-d\sigma/(\sigma+\varphi)})$.
Taking Bini's algorithm as an example, we have $\sigma=\varphi=1$, so the error is $O(2^{-d/2})$, or the square root of working precision.
Note that if multiple recursive steps are used, then $\varphi$ increases proportional to the number of steps, so straightforward optimization of $\lambda$ results in error of $O(2^{-d\sigma/(\sigma+s\varphi)})$ for $s$ recursive steps.

@@

\subsection{APA Algorithm Properties}

>>>>

\author{\IEEEauthorblockN{Grey Ballard}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{ballard@wfu.edu}}
\and
\IEEEauthorblockN{Jack Weissenberger}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{jack.weissenberger@gmail.com}}
\and
\IEEEauthorblockN{Luoping Zhang}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston Salem, NC, USA \\
\email{zhanl317@wfu.edu}}
}

@@

Given these two contributions to the numerical error, $\lambda$ can be optimized to balance the effects based on parameters $\sigma$ and $\varphi$ (and $d$).
As shown by Bini, Lotti, and Romani \cite{BLR80}, the optimal $\lambda$ should be set to $\Theta(2^{-d/(\sigma+\varphi)})$.
Using this value of $\lambda$, the numerical error incurred by the algorithm will be bounded by $O(2^{-d\sigma/(\sigma+\varphi)})$.
Taking Bini's algorithm as an example, we have $\sigma=\varphi=1$, so the error is $O(2^{-d/2})$, or the square root of working precision.
Note that if multiple recursive steps are used, then $\varphi$ increases proportional to the number of steps, so straightforward optimization of $\lambda$ results in error of $O(2^{-d\sigma/(\sigma+s\varphi)})$ for $s$ recursive steps.
The parameters and minimum error for the algorithms we consider are presented in \cref{sec:APAprops}.
We show empirical error results for uniform random inputs of varying dimension in \cref{fig:accuracy}, as compared to the classical algorithm.
\GB{add more details on experiment here...}

\begin{figure}
\centering
\renewcommand{\datafile}{data/accuracy.dat}
\input{plots/accuracy}
\caption{Relative Frobenius norm error for APA algorithms on random inputs.}
\label{fig:accuracy}
\end{figure}

@@

\subsection{APA Algorithm Properties}
\label{sec:APAprops}
